Fractional Types

### 2013-02-17 frac.tex
added explanation of implicit premises

>>>>

The operational semantics define a relation rather than a function, now, but the
goal is for them to still be reversible; in particular, we wish for the relation
to mode check so that for any combinator {{c}} we can treat either its left or
its right side as an input; this allows us to define {{sym}} as just an argument
swap. In the interest of brevity, we have treated the type annotations in the
base isomorphisms as implicit; for example, the rule for {{assocr*}} should
really read

%subcode{proof} include main
%@ v1 in b1
%@ v2 in b2
%@ v3 in b3
%@@ ((v1, v2), v3) ~~assocr*_{b1, b2, b3}~~ (v1, (v2, v3))
